Trees_making_solutions

### 2019-02-07 R/Data_extractions_solutions.Rmd
reorganised

**ANSWER 4:**    
 1. Non-informative column names (which group should be nr 1 ?)   
 2. Second study has non-numerical values in the columns that should be numerical (NA is good for missing values, but should be used consistently)    
 3. Species column is a mix of Latin and common names (should be all Latin)   
 4. There is an extra dot in " 6.4      .""

**ANSWER 5:**    
CohortID is used to indicate that the same cohorts/group of animals, of different sex (F, M), were measured repeatedly at different ages (60 and 120). These are not independent data points, and this is captured by CohortID. For different study question this could be an unique identifier of various study sites or populations that need tp be distinguished within and between studies.

@@

**ANSWER 9:**    
Meta-data is a detailed description of all extracted variables/columns and all other variables/columns derived from them. More specifically it describes how the data was coded (e.g. the measurement units, how conversions were made, any decisions and assumptions that had to be made in general for a given column of data"; e.g. whether sex was coded as "F" and "M" and "B", and what these values mean, jhow missing values were coded, and anything else that would allow you or somebody to extract and code the same data). Meta-data is an essential part of the documentation of your meta-analysis and it is extremely useful when you or somebody else checks the data or tries to re-analyse or re-use it. It is a good practice to start creating such documentation when you start extractions and coding and update it as you make changes and progress to analyses.

>>>>

**ANSWER 4:**    
 1. Non-informative column names (which group should be N 1 ?)  and column names should be one string (word) 
 2. Second study has non-numerical values in the columns that should be numerical (NA is good for missing values, but should be used consistently)    
 3. Species column is a mix of Latin and common names (should be all Latin)   
 4. There is an extra dot in " 6.4      .""

**ANSWER 5:**    
CohortID is used to indicate that the same cohorts/group of animals, of different sex (F, M), were measured repeatedly at different ages (60 and 120). These are not independent data points, and this is captured by CohortID. For different study question this could be an unique identifier of various study sites or populations that need to be distinguished within and between studies.

@@

**ANSWER 9:**    
Meta-data is a detailed description of all extracted variables/columns and all other variables/columns derived from them. More specifically it describes how the data was coded (e.g. the measurement units, how conversions were made, any decisions and assumptions that had to be made in general for a given column of data"; e.g. whether sex was coded as "F" and "M" and "B", and what these values mean, how missing values were coded, and anything else that would allow you or somebody to extract and code the same data). Meta-data is an essential part of the documentation of your meta-analysis and it is extremely useful when you or somebody else checks the data or tries to re-analyse or re-use it. It is a good practice to start creating such documentation when you start extractions and coding and update it as you make changes and progress to analyses.

### 2019-02-07 R/Trees_making_solutions.Rmd
reorganised

Quercus_treebase <- search_treebase(Quercus3sp_string, by=c("taxon","taxon","taxon"), max_trees=10, exact_match = TRUE, only_metadata = TRUE) #note different commas than in the treebase tutorial!
t(data.frame(matrix(unlist(Quercus_treebase), nrow=6, byrow=F), row.names = c("S.id", "Tr.id", "type", "kind", "quality", "ntax"))) #note the study IDs that you are using - you can find these on Treebase
Quercuss_tree <- search_treebase("113123", by="id.tree", exact_match = TRUE) #returns a single tree in a list 
Quercuss_tree <- Quercuss_tree[[1]] #extract tree from the list
#if Treebase does not work use: Quercuss_tree <- read.nexus(file = "T113123.nex") #read Nexus tree file

# plot(Quercuss_tree, cex=.8, label.offset =.1, no.margin = TRUE) #a big tree of all sorts of trees - needs good trimming!
Quercus3sp_tree <- drop.tip(Quercuss_tree, Quercuss_tree$tip.label[-match(Quercus3sp, Quercuss_tree$tip.label)])
#plot(Quercus3sp_tree, cex=.8, label.offset =.1, no.margin = TRUE)

#check the overlap between species name from the data fila nad the tree file
intersect(as.character(Quercus3sp_tree$tip.label), Quercus3sp) # all matching, but we changed the species name in teh list, so it will no longer match the original dataset
Quercus3sp_tree$tip.label <- gsub("montana", "prinus", Quercus3sp_tree$tip.label) #replace the tip label back with our species name
Quercus3sp_tree$tip.label <- gsub("_"," ", Quercus3sp_tree$tip.label) #get rid of the underscores
```

@@

```{r graft Quercus_tree}
tree <- read.tree(file="tree_curtis1998.tre") #run if you need to read it in
tree_pruned <- drop.tip(tree, c("Quercus prinus", "Quercus alba")) #prune 3 species
tree_grafted <- bind.tree(tree_pruned, Quercus3sp_tree, where=which(tree_pruned$tip.label=="Quercus_rubra")) #graft 3 species to the remaining Acer species
```

>>>>

Quercus_treebase <- search_treebase(Quercus3sp_string, by=c("taxon","taxon","taxon"), max_trees=10, exact_match = TRUE, only_metadata = TRUE) #note different commas than in the treebase tutorial!
t(data.frame(matrix(unlist(Quercus_treebase), nrow=6, byrow=F), row.names = c("S.id", "Tr.id", "type", "kind", "quality", "ntax"))) #note the study IDs that you are using - you can find these on Treebase
Quercuss_tree <- search_treebase("113123", by="id.tree", exact_match = TRUE) #returns a single tree in a list 
Quercuss_tree <- Quercuss_tree[[1]] #extract tree from the list
#if Treebase does not work use: Quercuss_tree <- read.nexus(file = "T113123.nex") #read Nexus tree file
intersect(as.character(Quercuss_tree$tip.label), Quercus3sp) # all 3 are present and matching
# plot(Quercuss_tree, cex=.8, label.offset =.1, no.margin = TRUE) #a big tree of all sorts of trees - needs good trimming!
Quercus3sp_tree <- drop.tip(Quercuss_tree, Quercuss_tree$tip.label[-match(Quercus3sp, Quercuss_tree$tip.label)])
#plot(Quercus3sp_tree, cex=.8, label.offset =.1, no.margin = TRUE)

#check the overlap between species name from the data fila nad the tree file
intersect(as.character(Quercus3sp_tree$tip.label), Quercus3sp) # all matching, but we changed the species name in the list, so it will no longer match the original dataset
Quercus3sp_tree$tip.label <- gsub("montana", "prinus", Quercus3sp_tree$tip.label) #replace the tip label back with our species name
Quercus3sp_tree$tip.label <- gsub("_"," ", Quercus3sp_tree$tip.label) #get rid of the underscores
```

@@

```{r graft Quercus_tree}
tree <- read.tree(file="tree_curtis1998.tre") #run if you need to read it in
tree_pruned <- drop.tip(tree, c("Quercus_prinus", "Quercus_alba")) #prune 3 species
tree_grafted <- bind.tree(tree_pruned, Quercus3sp_tree, where=which(tree_pruned$tip.label=="Quercus_rubra")) #graft 3 species to the remaining Acer species
```
